\documentclass[a4paper]{srika-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

%\lastupdated % Print the Last Updated text at the top right

\namesection{SRIKANTH}{R}{ % Your name
{Backend Developer} \\
{\FA\faEnvelopeAlt} {\href{mailto:srikanthr.0402@gmail.com}{srikanthr.0402@gmail.com} | {\FA\faPhone} \href{tel:+919788536910}{+91-9788536910} | {\FA\faLinkedin} \href{http://www.linkedin.com/srikaram}{srikaram} | {\FA\faGithub} \href{http://www.github.com/rsri}{rsri}} % Your contact information 
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.35\textwidth} % The left column takes up 35% of the text width of the page

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}

\location{Proficient:}
\textbf{Java \textbullet{} Android \textbullet{} Spring \textbullet{} SQL (Sybase/Oracle) } \\
\location{Intermediate:}
\textbf{HTML5/CSS3 \textbullet{} Oracle ADF \textbullet{} JavaScript/jQuery \textbullet{} Python \textbullet{} Hibernate \textbullet{} Apache Qpid} \\
\location{Familiar:}
\textbf{iOS (Objective-C) \textbullet{} Docker \textbullet{} Bash scripting } \\

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 
\subsection{Karpagam college of Engineering}

\descript{BE - Computer Science and Engineering}
\location{April 2013 | Coimbatore, India | CGPA: 8.28}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Sri Gopal Naidu Higher Sec School}

\location{May 2009 | Coimbatore, India \\ Secondary school: 90.5\%}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{ABC Matric Higher Sec School}

\location{May 2007 | Coimbatore, India \\ High school: 87.7\%}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Github works
%------------------------------------------------

\section{Github projects}

\subsection {\href{https://github.com/rsri/GamesOfThronesC}{GOTC - A programming language}}

Programming language developed with Java where syntax and statements use dialogues and phrases from \textbf{Game of Thrones} show.

\sectionspace % Some whitespace after the section
%------------------------------------------------

\subsection{\href{https://github.com/rsri/Pic2Fro} {Pic2Fro - Windows moviemaker for Android}}

Android app to create a short length video using photos in gallery or using camera muxed with user-picked background audio.

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------
%------------------------------------------------
% Extra-curricular activities
%------------------------------------------------

\section{Extra-curricular activities} 
\begin{tightitemizespaced}
\item Won 'first' prize in 'Lateral and Logical thinking' event in an inter-school competition
\item Won 'first' prize intra-college 'Chess' tournament
\item Student coordinator in organizing “Ripple'12 \& Ripple'13, National Level Technical Symposiums”
\end{tightitemizespaced}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Hobbies
%------------------------------------------------

\section{Hobbies} 
\begin{tightitemizespaced}
\item Playing chess
\item Watching television series
\item Reading books
\item Badminton
\end{tightitemizespaced}

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.64\textwidth} % The right column takes up 64% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{JP Morgan Chase \& Co.}
\descript{| Associate}

\location{May 2018 – Present | Bangalore, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Working in the development of \textbf{Pyramid, strategic trade processing and risk system for Equity and Credit Derivatives} - specifically on Pyramid Trade Service, a Java/Spring based service system backed by Sybase database.
\item Service handles trade booking requests from various upstream systems and affirmation requests from platforms such as Markitwire/DTCC. 
\item Currently working on creating new outbound services for reporting the booked OTC (Over-the-counter) trades to corporate regulatory and supervisory bodies such as ESMA, FINMA.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Oracle India}
\descript{| Applications Engineer}

\location{Jul 2016 - May 2018 | Bangalore, India}
\begin{tightitemize}
\item Worked in the \textbf{\href{https://docs.oracle.com/cloud/latest/salescs_gs/OASAL/OASAL1439686.htm\#OASAL1439686}{Oracle Sales Cloud Assignment Manager}} team in Java with ADF and Oracle DB to develop an engine that assigns resources to business objects used by sales administrators to implement, configure, and use administrative components of the cloud service.
\item Implemented a workflow in the module where an assignment invocation would identify the matching candidate(s) for each work object that’s being assigned.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Impiger technologies}
\descript{| Senior Software Development Engineer}

\location{Sep 2013 – Jun 2016 | Coimbatore, India}
\begin{tightitemize}
\item Worked in \textbf{\href{https://en.wikipedia.org/wiki/Quickoffice}{Quickoffice, an Android Officesuite application}} development team
\item Developed several Android applications adhering to full SDLC.
\item Worked on a Python project named Resourcefully using HTML5 and CSS3 with JQuery incorporated within Django for employee projects tracker.
\item Worked on a J2EE project with Hibernate named RationalPipe to develop workflows, including downloading statistical data periodically, parse and save them in database. 
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Projects
%------------------------------------------------

\section{Projects}

\runsubsection{QUICKOFFICE}
\descript{| GOOGLE DOCS, SHEETS, SLIDES}

\location{Android, XML, Ant}
An OfficeSuite application that later got integrated into Google Apps that allows to
create, access and edit Word, Excel, and PowerPoint documents.\\
Implemented the feature to apply, view and remove \textbf{Styles} in Word documents. \\
Implemented several \textbf{Formulas} that can be inserted and used in Excel documents.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Resourcefully}

\location{HTML5, JavaScript, jQuery, Python, Django, MySQL}
An internal project used by managers for resource allocation along with management of projects, vacations and employees.  \\
Implemented the feature to add, edit and remove employees and eventually allocate them to a project depending on the manager the resource is under.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Rational Pipe}

\location{J2EE, Servlets, Hibernate, MySQL}
Worked as a part of team that developed workflows to download statistical data such as weather statistics from government websites periodically, parse and save them in database, which would be served to the client developed with Adobe Flex. 

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}